Air cargo load and route planning in pickup and delivery operations

### 2023-06-04 CAIE/paper.tex
Meta-heuristics created

The ACLP+RPDP solution defines a tour and a corresponding loading and unloading plan at each node. In this way, the loading and unloading time will be limited only by the use of the equipment at each node. Therefore, there will only be waiting time at the base node, corresponding to the runtime of ACLP+RPDP algorithm. For this reason, our method will also be parameterized by the maximum time that can be waited until the start of the load in the base node.

@@

$time$\/ is a runtime limit, which will be distributed among the node-by-node solutions (lines \ref{main:f1} and \ref{main:f2}). Each tour consists of $K+1$\/ trips, and the total number of tours is $K!$.

@@

$SolveTour$\/ is described in Algorithm \ref{alg:tour}, where $\pi$\/ is a permutation of the nodes (excluding the base) that defines the order of visits in this tour, $method$\/ corresponds to a MIP solver or a heuristic for solving the node-by-node problems, and $time$\/ is the runtime limit that will be distributed among the $K+1$\/ legs of the tour.

@@

The average values were presented for $f_{\pi}$\/ and, for the run time, the worst result obtained. To facilitate the comparison between the methods, we added a last column in these tables, where two values are indicated:
\begin{itemize}
	\item {\bf Normalized}: value between 0 and 1, which corresponds to the ratio between the sum of $f$\/ values obtained by the method in all scenarios and the sum of the best values obtained among all methods in all scenarios. The higher the value of {\bf Normalized}, the closer the method approached the best solutions found.
	\item {\bf Speed-up}: ratio of the sums of the worst runtimes of all scenarios and the sum of the method runtimes in all scenarios. The method with the highest {\bf Speed-up}\/ is the fastest.
\end{itemize}

@@

The upper bound is the objective function value of a linear programming relaxation of the problem, demonstrating that no integer viable solution can have an objective value greater (in maximization) than this.

@@

\begin{table}[H]
\centering
\caption{Methods and scenarios with $surplus =1.2$}  \label{tab:20}
\footnotesize
\begin{tabular}{c|c|ccccc|c}
\toprule
{$method$}      & {\bf Results}&{\bf 1}&{\bf 2} & {\bf 3}      & {\bf 4}      & {\bf 5}  & \specialcell{{\bf Normalized}\\{\bf Speed-up}}  \\
\midrule[.1pt]
\multirow{2}{*}{{\it Gurobi}}     & Upper bound for $f$      & {\it 7.91} & {\it 11.92} & {\it 13.12} & {\it 14.29} & {\it 13.34} & -  \\ %51,84
&{\bf run time (s)}                          & 14         & 19          & 73          & 188         & 1,097      & -  \\ 
\toprule
\multirow{2}{*}{\textbf{TS}}      & $f$      & 5.37       &             &             &             &            &   \\ % 5.49	 901
&{\bf run time (s)}                          & 659        &             &             &             &            &   \\ 
\midrule[.1pt]		
\multirow{2}{*}{\textbf{GRASP}}   & $f$      &            &             &             &             &            &   \\ 
&{\bf run time (s)}                          &            &             &             &             &            &   \\ 
\midrule[.1pt]
\multirow{2}{*}{\textbf{ACO}}     & $f$      & 5.25       & 5.75        & 5.06        & 4.84        &  4.20      &   \\ % 4.20	 1133
&{\bf run time (s)}                          & 313        & 326         & 303         & 256         &  1,133     &   \\ 
\midrule[.1pt]	
\multirow{2}{*}{\textbf{NMO}}     & $f$      &            &             &             &             &            &   \\
&{\bf run time (s)}                          &            &             &             &             &            &   \\ 
\midrule[.1pt]	
\multirow{2}{*}{\textbf{Shims}}   & $f$      & 7.91       & 11.55       & 12.62       &  13.82      &  14.85          &   \\ % 14.85	 563
&{\bf run time (s)}                          & 4          &  8          &  33         &  94         &  563          &   \\

>>>>

The ACLP+RPDP solution defines a tour and a corresponding loading and unloading plan at each node. In this way, the loading and unloading time will be limited only by the use of the equipment at each node. Therefore, there will only be waiting time at the base node, corresponding to the run time of ACLP+RPDP algorithm. For this reason, our method will also be parameterized by the maximum time that can be waited until the start of the load in the base node.

@@

$time$\/ is a run time limit, which will be distributed among the node-by-node solutions (lines \ref{main:f1} and \ref{main:f2}). Each tour consists of $K+1$\/ trips, and the total number of tours is $K!$.

@@

$SolveTour$\/ is described in Algorithm \ref{alg:tour}, where $\pi$\/ is a permutation of the nodes (excluding the base) that defines the order of visits in this tour, $method$\/ corresponds to a MIP solver or a heuristic for solving the node-by-node problems, and $time$\/ is the run time limit that will be distributed among the $K+1$\/ legs of the tour.

@@

The average values were presented for $f_{\pi}$\/ and, for the run time, the worst result obtained. To facilitate the comparison between the methods, we added a last column in these tables, where two values are indicated:
\begin{itemize}
	\item {\bf Normalized}: value between 0 and 1, which corresponds to the ratio between the sum of $f$\/ values obtained by the method in all scenarios and the sum of the best values obtained among all methods in all scenarios. The higher the value of {\bf Normalized}, the closer the method approached the best solutions found.
	\item {\bf Speed-up}: ratio of the sums of the worst run times of all scenarios and the sum of the method run times in all scenarios. The method with the highest {\bf Speed-up}\/ is the fastest.

	\item {\bf run time (s)} is the average time to solve a problem instance.
\end{itemize}

@@

The upper bound (UB) is the objective function value of a linear programming relaxation of the problem, demonstrating that no integer viable solution can have an objective value greater (in maximization) than this.

@@

\begin{table}[H]
\centering
\caption{Methods and scenarios with $surplus =1.2$}  \label{tab:20}
\footnotesize
\begin{tabular}{c|c|ccccc|c}
\toprule
$method$& {\bf Scenarios}                 &{\bf 1}&{\bf 2} & {\bf 3}      & {\bf 4}      & {\bf 5}  & \specialcell{{\bf Normalized}\\{\bf Speed-up}}  \\
\midrule[.1pt]
{\it Gurobi}     & UB for $f$           & {\it 7.91} & {\it 11.92} & {\it 13.12} & {\it 14.29} & {\it 13.34} & -  \\ %51,84
\toprule
\multirow{2}{*}{\it TS }      & $f$     & 5.37       & 5.86        & 5.25        & 4.62        & 3.60       &   \\ %  3.60	 86
&{\bf run time (s)}                          & 659        & 361         & 251         & 105         & 86         &   \\ 
\midrule[.1pt]		
\multirow{2}{*}{\it GRASP }   & $f$     & 8.35       & 11.94       & 12.89       & 14.10       & 12.98      &   \\ % 8.35	 97	
&{\bf run time (s)}                          & 97         & 156         & 222         & 109         & 105        &   \\ 
\midrule[.1pt]
\multirow{2}{*}{\it ACO}     & $f$      & 5.25       & 5.75        & 5.06        & 4.84        &  4.20      &   \\ % 4.20	 1133
&{\bf run time (s)}                          & 313        & 326         & 303         & 256         &  453       &   \\ 
\midrule[.1pt]	
\multirow{2}{*}{\it NMO}     & $f$      & 8.62       &             &             &             &            &   \\ 
&{\bf run time (s)}                          & 901        &             &             &             &            &   \\ 
\midrule[.1pt]	
\multirow{2}{*}{\it Shims}   & $f$      & 8.43       & 12.77       & 14.47       &  16.28      &  15.47          &   \\
&{\bf run time (s)}                     & 4          &  8          &  33         &  93         &  570          &   \\
